A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\section{PCA coupled with Linear Regression}\label{section:pca_linreg}

@@

\subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
Permeability can be represented as tensor quantity, but for the purpose of the following explanation (and the remaining of this paper), it is assumed that permeability is a scalar quantity. Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the simulation domain.

>>>>

\section{Coupled PCA and Linear Regression}\label{section:pca_linreg}

@@

\subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity. Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the simulation domain.
